---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# streamDepletr
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) [![Travis-CI Build Status](https://travis-ci.org/szipper/streamDepletr.svg?branch=master)](https://travis-ci.org/szipper/streamDepletr)

streamDepletr is an R package with functions for assessing the impacts of groundwater pumping on streams. There are two primary categories of functions:

- Analytical streamflow depletion models, which estimate the change in groundwater inputs to a stream resulting from pumping (`hunt`, `glover`, `hantush`, `intermittent_pumping`)
- Depletion apportionment equations, which distribute streamflow depletion estimating using the analytical models to different reaches within a stream network (`apportion_inverse`, `apportion_web`, `apportion_polygon`, `apportion_wedge`)

## Installation

You can install streamDepletr from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")  # uncomment if you don't alreayd have devtools
devtools::install_github("szipper/streamDepletr",
                         build_vignettes=T)
```

## Example

Calculate and plot streamflow depletion as a fraction of the pumping rate (`Qf`) over the 100 days of pumping:

```{r SamplePlot, fig.width=6, fig.height=6}
require(streamDepletr)

# calculate depletion fraction
Qf <- glover(t  = seq(1,100),     # timesteps to evaluate
             d  = 150,            # well to stream distance
             S  = 0.10,           # specific yield
             Tr = 50*1e-5*86400)  # 50 m thick aquifer with hydraulic conductivity of 1e-5 m/s

# plot
plot(seq(1,100), Qf, type="l", xlab="Time [days]", ylab="Qf, Streamflow Depletion Fraction")
```

For more examples, please check out the package vignette:

`browseVignettes("streamDepletr")`