---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# streamDepletr

streamDepletr is an R package with functions for assessing the impacts of groundwater pumping on streams. There are two primary categories of functions:

- Analytical streamflow depletion models, which estimate the change in groundwater inputs to a stream resulting from pumping (`hunt`, `glover`, `hantush`, `intermittent_pumping`)
- Depletion apportionment equations, which distribute streamflow depletion estimating using the analytical models to different reaches within a stream network (`apportion_inverse`, `apportion_web`, `apportion_polygon`, `apportion_wedge`)
- Data preparation functions to prepare inputs for the analytical models and depletion apportionment equations (`depletion_max_distance`, `prep_reach_dist`, `streambed_conductance`)

Combined, these functions will allow the user to estimate the impacts of an existing or proposed well (or group of wells) on individual stream reaches within a stream network.

## Installation

You can install streamDepletr from CRAN: `install.packages("streamDepletr")`

Alternately, you can use `devtools` to install the development version:
```{r gh-installation, eval = FALSE}
devtools::install_github("FoundrySpatial/streamDepletr", build_vignettes=T)
```

## Example

Calculate and plot streamflow depletion as a fraction of the pumping rate (`Qf`) over the 100 days of pumping:

```{r SamplePlot, fig.width=6, fig.height=6}
require(streamDepletr)

# calculate depletion fraction
Qf <- glover(t  = seq(1,100),     # timesteps to evaluate
             d  = 150,            # well to stream distance
             S  = 0.10,           # specific yield
             Tr = 50*1e-5*86400)  # 50 m thick aquifer with hydraulic conductivity of 1e-5 m/s

# plot
plot(seq(1,100), Qf, type="l", xlab="Time [days]", ylab="Qf, Streamflow Depletion Fraction")
```

For more examples, please check out the package vignette:

`browseVignettes("streamDepletr")`

## Package Development
streamDepletr was developed by Foundry Spatial Ltd. and the University of Victoria with support from the National Sciences and Engineering Research Council of Canada.